### 2021-01-07 paper/sections/design.tex
third response

\subsection{Problem Formulation}
\label{subsec: formulation}

% \colorbox{red}{notation table}
Without loss of generality, we denote the cloud-based deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $. It has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input image $ x \in X_{\rm ref} $. We use this $ \vec{y}_{\rm ref} $ as the ground truth label. For each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the top-5 accuracy as the following $ \mathcal{A} $, the same as the classification metric of ILSVRC2012~\cite{ILSVRC12}.

@@

\subsection{RL Agent Design}

The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size {\color{revise2}$ \hat{s}_c $} while keeping the accuracy $ \mathcal{A} $. {\color{revise2} In our design, each compression is treated as a complete RL task that only has one step, and the agent performs the action only once to accomplish the task. The agent is able to learn across consecutive tasks, because the input sequence (i.e., consecutive images likely to be captured by the same camera) shares similar contextual characteristics. The similar design has also been used in previous studies, including RL-based cache strategy \cite{wang2020intelligent_RL,zhong2018deep_RL,sadeghi2019deep_RL}.} For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $. Therefore we can use the Deep Q-learning Network as the RL agent. But the naive Deep Q-learning Network can not work well in this task because of the following challenges: %% \\

@@

We formulate the feature extractor's output {\color{revise2} $ s = \mathcal{E}(J(\mathcal{X}, c)) $} \iffalse $ \mathcal{E}(J(\mathcal{X}, c)) $ \fi as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}. In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $. We denote the \emph{action-value function} as {\color{revise2} $ Q(\mathcal{E}(f_t), c; \theta) $} \iffalse $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi and the optimal compression quality level at time $ t $ as {\color{revise2} $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $} \iffalse $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, i.e., there is no signal from the environment telling that an episode has finished. Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $. In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction and decreases the randomness when training afterward. {\color{revise2} In iteration $t$, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$. The RL agent $\phi$ generates a compresion quality level $c_t$. The framework compresses image $x_t$ at quality $c_t$ to upload and obtains reward $r_t$. Then the framework obtains the next image $x_{t+1}$ and generates the next state $ s_{t+1} = \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $. The framework stores transition $(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t )$ in a memory buffer $\mathcal{D}$. Especially, $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in the inference-estimation-querying-retraining mechanism to be discussed in Section \ref{subsec: mechanism}.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}.
% and we list the parameters in Section.~\ref{Section: evaluation}.

\begin{algorithm}[!t]
{\color{revise2}
	\caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
	\label{alg: rl-train}
	\begin{algorithmic}[1]
		\STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
		\STATE Initialize \emph{action-value function} $ Q $ with random weights $ \theta $
		{\color{revise2}
		\STATE Initialize state $ s_1 \leftarrow \mathcal{E}\big(J(x_1, c_{ref})\big), x_1 \in \mathcal{X} $ }
%		and $ \phi_1 = \phi(f_1) $
		\FOR {$t \in 1,2,\cdots, K$}
%		\STATE \textbf{1) Exploration.} %With probability $\epsilon$:
		\STATE \textbf{1) Exploration}
		\STATE With probability $\epsilon$:
		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
		\STATE Otherwise:
		{\color{revise2}
		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $ }
%		{\rm argmax}_cQ\Big(\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
		\STATE

@@

%		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
		\ENDIF
	    }
		\ENDFOR
	\end{algorithmic}
}
\end{algorithm}

@@

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Baidu_choices1.pdf}}
		\centerline{(a) Baidu Vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Facepp_choices1.pdf}}
		\centerline{(b) Face++}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Amazon_choices1.pdf}}
		\centerline{(c) Amazon Rekognition}
	\end{minipage}		
	\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different cloud services}}
	\label{fig: quality_chosen}
}
\end{figure*}

%\begin{figure}[!t]
%	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
%	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
%	\label{fig: quality_chosen}
%	% \vspace{-0.3cm}
%\end{figure}

@@

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
		\centerline{(a) ImageNet images}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
		\centerline{(b) FLIR images}
	\end{minipage}	
    \caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
	\label{fig: dataset_change}
}
\end{figure*}

>>>>

\vspace{-1em}

\subsection{Problem Formulation}
\label{subsec: formulation}
% \colorbox{red}{notation table}
Without loss of generality, we denote the cloud-based deep learning service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input image $ x_i $. It has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each reference input image $ x \in X_{\rm ref} $. We use this $ \vec{y}_{\rm ref} $ as the ground truth label. For each image $ x_c $ compressed at compression quality level $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the top-5 accuracy as the following $ \mathcal{A} $, the same as the classification metric of ILSVRC2012~\cite{ILSVRC12}.

@@

\subsection{RL Agent Design}
\label{RL Design}
The RL agent is expected to give a proper compression quality level $ c $ for minimizing the file size {\color{revise2}$ \hat{s}_c $} while keeping the accuracy $ \mathcal{A} $. {\color{revise2} In our design, each compression is treated as a complete RL task that only has one step, and the agent performs the action only once to accomplish the task. The agent is able to learn across consecutive tasks, because the input sequence (i.e., consecutive images likely to be captured by the same camera) shares similar contextual characteristics. The similar design has also been used in previous studies, including RL-based cache strategy \cite{wang2020intelligent_RL,zhong2018deep_RL,sadeghi2019deep_RL}.} For the RL agent, the input features are continuous numerical vectors, and the expected output is discrete compression quality level $ c $. Therefore we can use the Deep Q-learning Network as the RL agent. But the naive Deep Q-learning Network can not work well in this task because of the following challenges: %% \\

@@

{\color{revise3} We start by giving some basics on Markov decision processes (MDPs) \cite{MDP}, which is represented by a tuple $<S,C,P,R,\gamma>$, where $S$ denotes a set of possible states $s$, $C$ a set of feasible actions $c$, $P$ the set of state transition probabilities, $R$ a reward function, and $\gamma$ a discount factor. We formulate the feature extractor's output  $ s = \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}. In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $. We use $P_{ss'}^{c} = P \big[s' \mid s, c = \pi(s) \big]$ to denote the state transition probability from state $s$ to $s'$, where $\pi$ is a compression strategy mapping state to actions. We therefore obtain a sequence of states and actions $\{ s_1,c_1,s_2,...,c_{t-1},s_t \}$, and this formulation is a MDP.}

{\color{revise3} The goal of the agent is to interact with the emulator environment $ \{\mathcal{X}, M\} $ by selecting actions in a way that maximises future reward $R$. We define the future discounted reward at time t as $R_t = \sum_{\hat{t}=t}^{T'} \gamma^{\hat{t}-t}r_{\hat{t}}$ , where $T'$ is the step at which the task terminates. In our design, a compression task only has one step, detailed discussed in \ref{RL Design}}.

{\color{revise3} We denote the optimal \emph{action-value function} as the maximum expected reward $ Q^{*}(\mathcal{E}(f_t), c; \theta) = \max_{\pi} \mathbb{E} \big[R_t \mid s_t=s,c_t=c,\pi\big]$ to learn the optimal compression strategy $\pi$, where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. The optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $. Also, the optimal action-value function obeys an important identity known as the Bellman equation, and the optimal strategy is to select the action $c'$ maximising the expected value of $r + \gamma Q^{*}(s', c'; \theta) $ \cite{DQN}.}

%The basic idea behind many reinforcement learning algorithms is to estimate the action-value function, by using the Bellman equation as an iterative update $ Q(s, c; \theta_{i}) = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $.

%We denote the \emph{action-value function} as {\color{revise2} $ Q(\mathcal{E}(f_t), c; \theta) $} \iffalse $ Q(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi and the optimal compression quality level at time $ t $ as {\color{revise2} $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $} \iffalse $ c_t = {\rm argmax}_cQ(\phi(\mathcal{E}(f_t)), c; \theta) $ \fi where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $.

In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

Different from conventional reinforcement learning, the interactions between the agent and environment are infinite, i.e., there is no signal from the environment telling that an episode has finished. Therefore, we train the RL agent intermittently at a manual interval of $ T $ after the condition $ t \geq T_{\rm start} $ guaranteeing that there are enough transitions in the memory buffer $ \mathcal{D} $. In the training phase, the RL agent firstly takes some random trials to observe the environment's reaction and decreases the randomness when training afterward. {\color{revise2} In iteration $t$, we  leverage the feature extractor $\mathcal{E}$ to obtain state $s_t = \mathcal{E}(J(x_t,c_{ref}))$. The RL agent $\phi$ generates a compression quality level $c_t$. The framework compresses image $x_t$ at quality $c_t$ to upload and obtains reward $r_t$. Then the framework obtains the next image $x_{t+1}$ and generates the next state $ s_{t+1} = \mathcal{E}\big(J(x_{t+1},c_{ref})\big) $. The framework stores transition $(s_t, c_t, r_t, s_{t+1},\mathcal{A}_t )$ in a memory buffer $\mathcal{D}$. Especially, $(s_t, c_t, r_t, s_{t+1} )$ is used to compute the loss function, and $(r_t,\mathcal{A}_t )$ is used in the inference-estimation-querying-retraining mechanism to be discussed in Section \ref{subsec: mechanism}.} All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}.
% and we list the parameters in Section.~\ref{Section: evaluation}.

%\setlength{\textfloatsep}{0.8cm}
\begin{algorithm}[!t]
{\color{revise2}
	\caption{Training RL agent $ \phi $ in environment $ \{\mathcal{X}, M\} $}
	\label{alg: rl-train}
	\begin{algorithmic}[1]
		\STATE Initialize replay memory buffer $ \mathcal{D} $ to capacity $ N $
		\STATE Initialize \emph{action-value function} $ Q $ with random weights $ \theta $
		{\color{revise2}
		\STATE Initialize state $ s_1 \leftarrow \mathcal{E}\big(J(x_1, c_{ref})\big), x_1 \in \mathcal{X} $ }
%		and $ \phi_1 = \phi(f_1) $
		\FOR {$t \in 1,2,\cdots, K$}
%		\STATE \textbf{1) Exploration.} %With probability $\epsilon$:
		\STATE \textbf{1) Exploration}
		\STATE With probability $\epsilon$:
		\STATE \hspace{1em} $c_t \leftarrow$ a random valid value 
		\STATE Otherwise:
		{\color{revise2}
		\STATE \hspace{1em} $ c_t \leftarrow {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $ }
%		{\rm argmax}_cQ\Big(\big(\mathcal{E}(f_t)\big), c; \theta\Big) $
		\STATE

@@

%		\STATE Perform a gradient descent step on \\ $ \big(y_j - Q(\phi_j, c_j; \theta)\big)^2 $ according to~\cite{DQN}
		\ENDIF
	    }
		\ENDFOR
	\end{algorithmic}
}
\end{algorithm}
%\setlength{\textfloatsep}{0.8cm}

@@

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Baidu_choices1.pdf}}
		\centerline{(a) Baidu Vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Facepp_choices1.pdf}}
		\centerline{(b) Face++}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Amazon_choices1.pdf}}
		\centerline{(c) Amazon Rekognition}
	\end{minipage}		
	\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different cloud services}}
	\label{fig: quality_chosen}
}
\vspace{-0.2cm} 
\end{figure*}
%\vspace{-0.3cm}
%\begin{figure}[!t]
%	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
%	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
%	\label{fig: quality_chosen}
%	% \vspace{-0.3cm}
%\end{figure}

@@

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
		\centerline{(a) ImageNet images}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
		\centerline{(b) FLIR images}
	\end{minipage}	
    \caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
	\label{fig: dataset_change}
}
\vspace{-0.1cm} 
\end{figure*}

### 2021-01-07 paper/sections/evaluation.tex
third response

We carry out real-world experiments to verify our solution's performance. We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure. For the cloud-based deep learning services, we choose Baidu Vision, Face++ object detection services and Amazon Rekognition. In the experiments, we use two datasets mentioned before in Subsection~\ref{subsec:insight}. The ImageNet dataset indicates daytime scenery, and the FLIR Thermal Dataset indicates nighttime scenery. Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.

@@

Figure~\ref{fig: train_steps} presents the upload traffic load of the training and inference phase. To be more intuitionistic, we plot the size overhead {\color{revise2} $ \frac{\hat{s}}{\hat{s}_{\rm ref}} $} \iffalse $ \frac{s}{s_{\rm ref}} $ \fi as the $ y $-axis where {\color{revise2} $ \hat{s} $} is the real upload size of AdaCompress and {\color{revise2} $ \hat{s}_{\rm ref} $} is the benchmark upload size. Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress. From Figure~\ref{fig: train_steps}, we can see that as the training procedure runs, the upload image size decreases because the RL agent learns to choose better compression quality levels to upload less data. In the training phase, to train the agent while remaining a convincing recognition result, AdaCompress has to upload the original image along with the compressed image to the cloud-end, obtaining the real result and the reward feedback. Therefore the upload traffic load is even higher than the conventional solution. But once the training phase has finished, the upload traffic load is lower than the benchmark. As shown in Figure~\ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's. %% \\

\subsection{Size Reduction and Accuracy Performance}

@@

%\begin{figure}[!t]
%    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
%    \caption{AdaCompress's reaction upon scenery change}
%%    \vspace{-0.2cm}
%    \label{fig: running-retrain}
%\end{figure}
\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/running-retrain.pdf}
	\caption{AdaCompress's reactions upon scenery change}
	%    \vspace{-0.2cm}
	\label{fig: running-retrain}
\end{figure}

@@

>>>>

We carry out real-world experiments to verify our solution's performance. We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure. For the cloud-based deep learning services, we choose Baidu Vision, Face++ object detection services and Amazon Rekognition. {\color{revise3}For the compression framework, we choose the JPEG compression method and use PIL library \cite{pillow_benchmark} to complete the JPEG compression process, which can take the compression quality level input. Especially, each compression quality level represents a quantization table in JPEG compression standard \cite{jpeg}.} In the experiments, we use two datasets mentioned before in Subsection~\ref{subsec:insight}. The ImageNet dataset indicates daytime scenery, and the FLIR Thermal Dataset indicates nighttime scenery. Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.

@@

Figure~\ref{fig: train_steps} presents the upload traffic load of the training and inference phase. To be more intuitionistic, we plot the size overhead {\color{revise2} $ \frac{\hat{s}}{\hat{s}_{\rm ref}} $} \iffalse $ \frac{s}{s_{\rm ref}} $ \fi as the $ y $-axis where {\color{revise2} $ \hat{s} $} is the real upload size of AdaCompress and {\color{revise2} $ \hat{s}_{\rm ref} $} is the benchmark upload size. Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress. From Figure~\ref{fig: train_steps}, we can see that as the training procedure runs, the upload image size decreases because the RL agent learns to choose better compression quality levels to upload less data. In the training phase, to train the agent while remaining a convincing recognition result, AdaCompress has to upload the original image along with the compressed image to the cloud-end, obtaining the real result and the reward feedback. \textcolor{revise3}{Therefore the upload traffic load is even higher than the conventional solution, and the accuracy is locked to 1 because AdaCompress uses the original image’s prediction label as the output result.} But once the training phase has finished, the upload traffic load is lower than the benchmark. As shown in Figure~\ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's. %% \\
%Therefore the upload traffic load is even higher than the conventional solution.
\subsection{Size Reduction and Accuracy Performance}

@@

%\begin{figure}[!t]
%    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
%    \caption{AdaCompress's reaction upon scenery change}
%%    \vspace{-0.2cm}
%    \label{fig: running-retrain}
%\end{figure}
\begin{figure}[!t]
	\includegraphics[width=0.8\linewidth]{figures/running-retrain.pdf}
	\caption{AdaCompress's reactions upon scenery change}
	%    \vspace{-0.2cm}
	\label{fig: running-retrain}
\vspace{-0.1cm} 
\end{figure}

@@

\subsection{Applicability for Different Image Compression Methods}

{\color{revise3} In our experiment, we choose the JPEG compression method as the compression framework. Furthermore, our framework is applicative for different image compression techniques, both traditional compression methods and neural network-based learned compression methods. Existing traditional compression methods all have an optional compression level, e.g., JPEG and WebP have the compression quality level, H.265/HEVC \cite{hevc} and H.266/VVC \cite{vvc} have the quantization parameter (QP). Neural network-based learned image compression is a Lagrangian multiplier-based rate-distortion optimization, which commonly has a tradeoff parameter that controls the rate-distortion tradeoff \cite{endtoend1,endtoend2,endtoend3,endtoend4}. Different values are corresponding to different bit rates. We can regard this tradeoff parameter as the compression level. These different compression techniques all can flexibly take a compression level as the input.}

### 2021-01-07 paper/sections/relatedwork.tex
third response

Based on these insights, Robert et al.~\cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder. Chao et al.~\cite{chao2011preserving} proposed using variable quantization, which is supported by the JPEG standard extension syntax~\cite{dis199110918} to compress the macroblocks in images. Furthermore, they~\cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance while reducing the image size overhead effectively. Liu et al.~\cite{DeepN-JPEG} proposed DeepN-JPEG that re-designs the quantization table by linking statistical information of defined features and defined quantization values so that the compressed image size is reduced for deep learning models. Chamain et al.~\cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000~\cite{rabbani2002jpeg2000} encoded images. Recently, Lionel et al.~\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform coefficients in the middle of the JPEG codec. Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images. %% \\

However, such proposals all need one to understand the characteristics of the cloud-based deep learning model and have access to the original training dataset,  \emph{generating} the appropriate compression schemes. To the best of our knowledge, we are the first to propose an adaptive compression configuration solution that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures.

In this journal extension, we improve the previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly. Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).

%Liu et al.~\cite{DeepN-JPEG} developed the DeepN-JPEG framework, a deep %neural network favorable JPEG-based image compression framework.

>>>>

Based on these insights, Robert et al.~\cite{torfason2018towards} tried to train the deep neural network from the compressed representations of an auto-encoder. Chao et al.~\cite{chao2011preserving} proposed using variable quantization, which is supported by the JPEG standard extension syntax~\cite{dis199110918} to compress the macroblocks in images. Furthermore, they~\cite{chao2013design} designed a quantization table based on the observed impact of scale-space processing on the discrete cosine transform (DCT) basis functions for JPEG images, achieving similar inference performance while reducing the image size overhead effectively. Liu et al.~\cite{DeepN-JPEG} proposed DeepN-JPEG that re-designs the quantization table by linking statistical information of defined features and defined quantization values so that the compressed image size is reduced for deep learning models. Chamain et al.~\cite{2019quannet} proposed a joint optimization of image classification network coupled with the image quantization, achieving image size reduction of JPGE2000~\cite{rabbani2002jpeg2000} encoded images. Recently, Lionel et al.~\cite{gueguen2018faster} presented a new type of neural network that infers directly from the discrete cosine transform coefficients in the middle of the JPEG codec. Baluja et al.~\cite{baluja2019task} proposed task-specific compression that compresses images based on the end-use of images. {\color{revise3}Yang et al.~\cite{endtoend} suggested using a powerful regularization to optimize the loss function in the end-to-end compression framework by considering the downstream perception task.} %% \\

{\color{revise3}However, such proposals all need one to understand the characteristics of the cloud-based deep learning model or details of the compression framework, and have access to the original training dataset, \emph{generating} the appropriate compression schemes. To the best of our knowledge, we are the first to propose an adaptive compression configuration solution that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures and the compression framework.}

In this journal extension, we improve the previous \emph{inference-estimate-retrain} mechanism to cut down the upload image size overhead effectively, add DeepN-JPEG comparative experiment, and amend the manuscript significantly. Especially in the DeepN-JPEG comparative experiment, since Liu et al.~\cite{DeepN-JPEG} evaluated the DeepN-JPEG framework on ImageNet by using four state-of-the-art DNN models (AlexNet~\cite{AlexNet-krizhevsky2012imagenet}, VGG~\cite{VGG-simonyan2014very}, GoogLeNet~\cite{GoogleNet-szegedy2015going} and ResNet~\cite{ResNet-he2016deep}) on local edge devices, which are different from online computer vision-based services, for comparison purpose, we implement the DeepN-JPEG framework according to their paper and evaluate the size reduction and accuracy performance using ImageNet and the metrics in Subsection~\ref{subsec:metrics} on three cloud-based deep learning services (Amazon Rekognition, Face++ and Baidu Vision).
%Liu et al.~\cite{DeepN-JPEG} developed the DeepN-JPEG framework, a deep %neural network favorable JPEG-based image compression framework.
